SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-14 paper/encoding.tex
cnf
experiments-table-versions-encoding

\subsubsection{Regulation on nodes and edges}
Regulation of a model is based on the kind of the model under consideration. for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by SNARE-SNARE inhibition.

@@

A1: SNARE-SNARE inhibition. Inhibition of the edges are driven by the pairing matrix.
\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]

@@

\subsubsection{Basic constraints on the edges and nodes}
The edge labels are subset of the node label of source and target compartment. \newline

@@

\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset a_{i,k} \, \]

@@

\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset a_{j,k} \, \]  
%C1 =  e_ijk -> aik and e_ijk -> ajk

@@

\subsubsection{Main constraints}
Main constraints to be followed. \newline

@@

\subsubsection{Steady state specification}
Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.

\subsubsection{Reachability definition and stability condition}
If molecule is active on an edge then it should be present on the edge. \newline

@@

\subsubsection{ Fusion rule Formula}

@@

\begin{enumerate}
\item  A \textbf{SNARE pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate SNARE activity based on the presence/absence of other molecules on the corresponding node or edge.
\end{enumerate}

@@

\[ \bigwedge\limits_{i,j,k} b_{i,j,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]

\subsubsection{Connectivity}
To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph. We can go down or up using -C \_ option.  \newline

>>>>

\subsubsection{Regulation on nodes and edges}
Regulation of a model is based on the kind of the model under consideration. for example model 1 (-V 1) has two different arbitrary Boolean function dictating the activity of the molecules on edge and nodes and for variation 3 (-V 3) activity on edge is driven by pairing inhibition.

@@

A1: Pairing inhibition. Inhibition of the edges are driven by the pairing matrix.
\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]

@@

\subsubsection{Constraints on the structure of the edges, nodes and pairing matrix}

@@

\[ \bigwedge\limits_{i,j,k} e_{i,j,k} \supset n_{i,k} \, \]

@@

\[ \bigwedge\limits_{i,q}  e_{i,j,k} \supset n_{j,k} \, \]  
%C1 =  e_ijk -> aik and e_ijk -> ajk

@@

\subsubsection{Constraints on presence and activity of the molecule}
Few additional constrints are required on the molesules presence and activity. \newline

@@

\subsubsection{Constraints for stability condition}
The whole cell should be in stable condition i.e global flow of the molecule is balanced at every point. Each molecule leaving the node on a vesicle should come back to its source node in a cycle, i.e., \textbf{for every molecule leaving the node there exists a cycle with that molecule present on \textit{each of the edges and nodes} of the path taken}.

\bf{Reachability definition and stability condition}
We have encoded this requiremnt by using reachability definition. 
If molecule is active on an edge then it should be present on the edge. \newline

@@

\subsubsection{Fusion rule constraints}

@@

\begin{enumerate}
\item  A \textbf{Pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
\item \textbf{Regulatory mechanisms} on edges and on nodes (possibly distinct) which regulate molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
\end{enumerate}

@@

\[ \bigwedge\limits_{i,j,q,k} b_{i,j,q,k} \supset \neg \bigvee_{j \neq j^{\prime}, k^{\prime\prime}} ( a_{j^{\prime},k^{\prime\prime}} \land p_{k,k^{\prime\prime}}) \, \]

\subsubsection{Graph connectivity constraints}
To check the whether that n connected is necessary condition, we remove (drop) n edges from the graph and if it disconnects the graph and we get an assignment we have a n connected satisfying graph. We can go down or up using -C \_ option.  \newline

### 2017-06-14 paper/experiments.tex
experiments-table-versions-encoding

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}
\begin{itemize}
\item 
\end{itemize}

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.
%
\input{tbl-qf-graph}
In table~\ref{tbl:qf-results}

>>>>

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}

\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\item Version F with additional constraint that every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
\item Version F but self-edges are allowed.
\end{enumerate}

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.

\input{tbl-qf-graph}
In table~\ref{tbl:qf-results} 
\b PARTIAL ...

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|l|l|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline
E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
C. & None & Boolean function & 3-connected & 3-connected \\  \hline
F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
D. & None & Pairing inhibition & No graph & No graph \\ \hline
B. & Boolean function & None & No graph & No graph \\ \hline
A. & None & None & No graph & No graph \\ \hline
G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline

  \end{tabular}
\label{table1}
\end{table}
